Model of lens candidates from Space Warps CFHTLS

### 2016-07-06 paper2.tex
editing

The candidates successfully modelled are all galaxies, with inferred
lensing masses ranging from $\sim10^{11}M_\odot$ to $>10^{13}M_\odot$.
Stellar masses have also been estimated, using photometry from the
CFHTLS pipeline and stellar-population models.  The trend well-known
in nearby galaxies, that star-formation efficiency is maximal for
total masses of $\approx10^{12}M_\odot$ and reduces for both lower and
higher masses, is discernable also in these much more distant
galaxies.
\end{abstract}

@@

Recent searches through the CFHTLS \citep{2012SPIE.8448E..0MC} using
arc-finders
\citep{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G} by
machine learning \citep{2016arXiv160504309P} and by visual inspection
\citep{2016MNRAS.455.1191M} have between them discovered an average of
four lenses per square degree.  So one can be optimistic about finding
many thousands of lenses in the next generation of wide-field surveys.
But modelling them all will be very difficult if the process is
labour-intensive.

One possibility is to enlist the help of citizen-scientists for
modelling large samples of lenses.  \cite{2015MNRAS.447.2170K}
developed a system whereby experienced but non-professional lens
enthusiasts can model newly-discovered lenses collaboratively.

>>>>

The candidates successfully modelled are all galaxies, with inferred
lensing masses ranging from $\sim10^{11}M_\odot$ to $>10^{13}M_\odot$.
Stellar masses have also been estimated, using photometry from the
CFHTLS pipeline and stellar-population models.  A trend well-known
in nearby galaxies, that star-formation efficiency is maximal for
total masses of $\approx10^{12}M_\odot$ and reduces for both lower and
higher masses, is discernable also in these much more distant
galaxies.
\end{abstract}

@@

Recent searches through the CFHTLS \citep{2012SPIE.8448E..0MC} using
arc-finders
\citep{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G} by
machine learning \citep{2016arXiv160504309P} and by visual inspection
by a citizen-science volunteers
\citep[Space~Warps][]{2016MNRAS.455.1171M,2016MNRAS.455.1191M} have
between them discovered an average of four lenses per square degree.
So one can be optimistic about finding many thousands of lenses in the
next generation of wide-field surveys.  But modelling them all will be
very difficult if the process is labour-intensive.

\cite{2015MNRAS.447.2170K} developed a new lens-modelling strategy
developed, designed to be scaleable to much larger lens samples.  The
idea was to collaborate with experienced members of the
citizen-science community, who had already participated in lens
discovery through Space~Warps, as well as several other projects
involving astronomical data.  The

One idea for coping with the challenge of modelling many more lenses
is to enlist the help of citizen scientists, a comm

 have between them discovered an average of
